### 2016-09-27 rebuttal.tex

\begin{solution}
We have added a citation for mpmath.
\end{solution}
\end{questions}

\section{Reviewer 3}

\begin{questions}
\question I suggest a major rewrite of the paper, to improve the structure and group differently approached subjects. It would probably be best to:
\begin{enumerate}
\item Create a new section (following the introduction of SymPy) on projects that use SymPy, and put in it the materials currently available in supplement's sections 8, 9, 11. The comparison with Mathematica (supplement's section 10) should be moved either to the introduction as a section, or right after the introduction as its own section, but it should not be in the middle of the description of SymPy-powered projects.
\item  This should be followed by the list of SymPy packages and modules (currently section 3) and descriptions of selected modules (currently sections 3.1, 3.3, 3.5, supplement's sections 5, 7, and 9).
\item Now, basic usage can be given as its own section (currently done in sections 2.1 and 2.3), followed by introductions on usage of various modules (currently in sections 3.2, 3.4, 3.6, 4, 5, and supplement's sections 2, 3, 4, 6).
\item In-depth architecture (most of the so far unmentioned sections) can be given either as its own section, or made into a supplement of its own (as it is naturally far more technical and less interesting to general audience).
\item The current conclusion works fine as the finishing section of the paper.
\end{enumerate}
\begin{solution}
  We have made the following changes to the paper

  \begin{enumerate}
  \item We have renamed the ``Features'' section to ``Overview of
    Capabilities''.
  \item We have renamed the ``Domain Specific Submodules'' section to
      ``Physics Submodule'' (see point~\ref{rev3point30}).
  \item We have moved the ``Architecture'' section to the end, after the
    ``Physics Submodule'' section.
  \item We have moved the ``Basic Usage'' subsection to the beginning of the
    ``Overview of Capabilities'' section, and added an intro paragraph to the
    ``Overview of Capabilities'' section.
  \item We have moved the ``Assumptions'' subsection to the ``Overview of
    Capabilities'' subsection, after the features table.
  \item The ``Comparison with Mathematica'' section has been moved to the end of
    the supplement.
  \item The ``Other Projects that
      Depend on SymPy'' section (which has been renamed from ``Other Projects that
      Use SymPy'') has been moved from the supplement to the main paper content.
  \end{enumerate}

### 2016-09-27 numerics.tex
small change about mpfr

Like SymPy, mpmath is a pure Python library.  A design decision of SymPy is to
keep it and its required dependencies pure Python. This is a primary advantage
 of mpmath over other multiple precision libraries such as GNU MPFR~\cite{Fousse:2007:MMB:1236463.1236468},
which is much more feature-rich and fast.  Like SymPy, mpmath is also BSD
licensed (GNU MPFR is licensed under the GNU Lesser General Public License~\cite{rosen2005open}).

>>>>

Like SymPy, mpmath is a pure Python library.  A design decision of SymPy is to
keep it and its required dependencies pure Python. This is a primary advantage
 of mpmath over other multiple precision libraries such as GNU MPFR~\cite{Fousse:2007:MMB:1236463.1236468},
which is faster.  Like SymPy, mpmath is also BSD
licensed (GNU MPFR is licensed under the GNU Lesser General Public License~\cite{rosen2005open}).
